---
title: "Afrozensus Dashboard"
output: 
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed
    theme: journal
runtime: shiny
---

```{r setup, include=FALSE, message=FALSE}
require(flexdashboard)
require(rpivotTable)
require(dplyr)
require(ggplot2)
require(htmlwidgets)
require(plotly)
require(gridExtra)
require(grid)
require(stringr)
df <- readRDS("dataAZ_synth.RDS")
```

Datentafel
=====================================
```{r}
varSelectInput("variables", "Variablen:", df, multiple = TRUE)

renderRpivotTable({df %>% dplyr::select(!!!input$variables) %>% rpivotTable(df, aggregatorName = "Count", rendererName = "Table")})
```

Demografie
=====================================

Column
-----------------------------------------------------------------------

### Bivariate Verteilung (Bar Graph)

```{r}
fluidRow(column(4,
selectInput(inputId="vars_1", label="Variable", choices=names(df[,c(680:866)]))),

column(4, selectInput(inputId="vars_2", label="Gegenueber...", choices=names(df[,c(680:866)]))))

renderPlotly({
  dem1 <- ggplot(df, aes(x=as.factor(!!as.name(input$vars_1)), fill=as.factor(!!as.name(input$vars_2)))) +
  geom_bar(position="fill", stat="count") +
  theme_minimal() +
  ylab("Prozent") +
  xlab("") +
  scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  dem1 <- ggplotly(dem1, height = 750)
  dem1
  })
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Histogramme (Univariat)
```{r}
renderPlotly({
dem2<-  ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_1)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

dem3 <- ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_2)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

subplot(list(dem2,dem3), nrows=2, shareY=TRUE, margin = 0.07)
})
```

### Kreisdiagramme (Univariat)
```{r}
renderPlot({
dem4<-  ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_1)), fill=as.factor(!!as.name(input$vars_1)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

dem5 <- ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_2)), fill=as.factor(!!as.name(input$vars_2)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

grid.arrange(dem4, dem5, ncol = 1)
})
```

Engagement
=====================================

Column
-----------------------------------------------------------------------

### Bivariate Verteilung (Bar Graph)

```{r}
fluidRow(column(4,
selectInput(inputId="vars_eng1", label="Variable", choices=names(df[,c(4:55)]))),

column(4, selectInput(inputId="vars_eng2", label="Gegenueber...", choices=names(df[,c(680:866)]))))

renderPlotly({
  dem1 <- ggplot(df, aes(x=as.factor(!!as.name(input$vars_eng1)), fill=as.factor(!!as.name(input$vars_eng2)))) +
  geom_bar(position="fill", stat="count") +
  theme_minimal() +
  ylab("Prozent") +
  xlab("") +
  scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  dem1 <- ggplotly(dem1, height = 750)
  dem1
  })
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Histogramme (Univariat)
```{r}
renderPlotly({
dem2<-  ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_eng1)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

dem3 <- ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_eng2)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

subplot(list(dem2,dem3), nrows=2, shareY=TRUE, margin = 0.07)
})
```

### Kreisdiagramme (Univariat)
```{r}
renderPlot({
dem4<-  ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_eng1)), fill=as.factor(!!as.name(input$vars_eng1)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

dem5 <- ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_eng2)), fill=as.factor(!!as.name(input$vars_eng2)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

grid.arrange(dem4, dem5, ncol = 1)
})
```


Diskriminierungserfahrungen
=====================================

Column
-----------------------------------------------------------------------

### Bivariate Verteilung (Bar Graph)

```{r}
fluidRow(column(4,
selectInput(inputId="vars_disk1", label="Variable", choices=names(df[,c(56:595)]))),

column(4, selectInput(inputId="vars_disk2", label="Gegenueber...", choices=names(df[,c(680:866)]))))

renderPlotly({
  dem1 <- ggplot(df, aes(x=as.factor(!!as.name(input$vars_disk1)), fill=as.factor(!!as.name(input$vars_disk2)))) +
  geom_bar(position="fill", stat="count") +
  theme_minimal() +
  ylab("Prozent") +
  xlab("") +
  scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  dem1 <- ggplotly(dem1, height = 750)
  dem1
  })
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Histogramme (Univariat)
```{r}
renderPlotly({
dem2<-  ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_disk1)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

dem3 <- ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_disk2)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

subplot(list(dem2,dem3), nrows=2, shareY=TRUE, margin = 0.07)
})
```

### Kreisdiagramme (Univariat)
```{r}
renderPlot({
dem4<-  ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_disk1)), fill=as.factor(!!as.name(input$vars_disk1)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

dem5 <- ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_disk2)), fill=as.factor(!!as.name(input$vars_disk2)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

grid.arrange(dem4, dem5, ncol = 1)
})
```


Wissen (Rechte & Institutionen)
=====================================

Column
-----------------------------------------------------------------------

### Bivariate Verteilung (Bar Graph)

```{r}
fluidRow(column(4,
selectInput(inputId="vars_wiss1", label="Variable", choices=names(df[,c(597:637)]))),

column(4, selectInput(inputId="vars_wiss2", label="Gegenueber...", choices=names(df[,c(680:866)]))))

renderPlotly({
  dem1 <- ggplot(df, aes(x=as.factor(!!as.name(input$vars_wiss1)), fill=as.factor(!!as.name(input$vars_wiss2)))) +
  geom_bar(position="fill", stat="count") +
  theme_minimal() +
  ylab("Prozent") +
  xlab("") +
  scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  dem1 <- ggplotly(dem1, height = 750)
  dem1
  })
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Histogramme (Univariat)
```{r}
renderPlotly({
dem2<-  ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_wiss1)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

dem3 <- ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_wiss2)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

subplot(list(dem2,dem3), nrows=2, shareY=TRUE, margin = 0.07)
})
```

### Kreisdiagramme (Univariat)
```{r}
renderPlot({
dem4<-  ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_wiss1)), fill=as.factor(!!as.name(input$vars_wiss1)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

dem5 <- ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_wiss2)), fill=as.factor(!!as.name(input$vars_wiss2)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

grid.arrange(dem4, dem5, ncol = 1)
})
```



Diskriminierung & Handlungsbedarfe
=====================================

Column
-----------------------------------------------------------------------

### Bivariate Verteilung (Bar Graph)

```{r}
fluidRow(column(4,
selectInput(inputId="vars_bed1", label="Variable", choices=names(df[,c(639:678)]))),

column(4, selectInput(inputId="vars_bed2", label="Gegenueber...", choices=names(df[,c(680:866)]))))

renderPlotly({
  dem1 <- ggplot(df, aes(x=as.factor(!!as.name(input$vars_bed1)), fill=as.factor(!!as.name(input$vars_bed2)))) +
  geom_bar(position="fill", stat="count") +
  theme_minimal() +
  ylab("Prozent") +
  xlab("") +
  scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
  dem1 <- ggplotly(dem1, height = 750)
  dem1
  })
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Histogramme (Univariat)
```{r}
renderPlotly({
dem2<-  ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_bed1)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

dem3 <- ggplotly(ggplot(df, aes(as.factor(!!as.name(input$vars_bed2)))) + geom_bar() + ylab("Haeufigkeit") + scale_x_discrete(label = function(x) stringr::str_trunc(x, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)))

subplot(list(dem2,dem3), nrows=2, shareY=TRUE, margin = 0.07)
})
```

### Kreisdiagramme (Univariat)
```{r}
renderPlot({
dem4<-  ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_bed1)), fill=as.factor(!!as.name(input$vars_bed1)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

dem5 <- ggplot(df, aes(x="", y=as.factor(!!as.name(input$vars_bed2)), fill=as.factor(!!as.name(input$vars_bed2)))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.title = element_blank())

grid.arrange(dem4, dem5, ncol = 1)
})
```
